\chapter{Introduction}
 
 \section{Description}
Developing advanced graphical applications is a very time-consuming and complex task that require experienced technical engineers with a solid background in computer science. [Bygga vidare på det här, alt. skriva om för att fylla ut]

Effects such as blinn/phong-lighting, shadow mapping, bloom filters etc. are very common and frequently implemented in various projects in the computer graphics realm. While shader code is easy to reuse, it often requires a programmer who knows the intended framework by heart to implement. An artist who quickly wants to see their models/textures/leveldesign/etc with in-game lighting, or with whatever effects the engine supports, might face difficulties because of the extra overhead caused by [aoaoaoaoa]. 

[Övergång till nästa stycke, något om DERP typ]

The DERP Editor is a content creation system that enables a user to build materials and post-processing rendering effects for 3D applications. The system is composed of several independent modules in a plug-in based architecture. The DERP editor is a small, standalone, easy-to-use piece of software with an intuitive graphical user interface, targeted towards advanced users experienced in the field of computer graphics. However, as the editor is built with simplicity in mind, it could be used by anyone starting out in computer graphics for the first time, or by a visual artist with no programming background or as a means of rapid development. 

\section{Motivation}
[Det här känns lite fattigt..]

Tools with similar functionality as DERP can often be found within various other modern 3D engines and packages such as Autodesk Maya 3D or the Unreal Engine 3. However, most such applications are proprietary, bound to other products and often quite costly. 
 
Furthermore, this project plans to expand upon these ideas and hopefully introduce new functionality. We consider our approach to be more dynamic and expandable, due to the plug-in based architecture. 
 
From an academic point of view, this project is an excellent opportunity in order to gain valuable experience in developing unique / interesting ideas in a contemporary environment. 
 